\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-12 conclusion.tex
conclusion

I would like to give my foremost thanks to Dr. Philip Guo, who very thoughtfully reached out to \emph{me} about using Skedge for research, reigniting its development. I also want to give enormous thanks to Ani and Mark Gabrellian for their generous Mesrob Mashtots Innovation Grant donation which funded Skedge's development in the summer of 2015. Finally, a huge thanks to all those students and my close friends who reported bugs, gave feedback, and in general supported, promoted, got excited about, and complained about Skedge!

>>>>

I would like to give my foremost thanks to Dr. Philip Guo, who very thoughtfully reached out to \emph{me} about using Skedge for research, and whose deep care and support for the project has since reignited and bloomed its development. I also want to give enormous thanks to Ani and Mark Gabrellian for their generous Mesrob Mashtots Innovation Grant donation which funded Skedge's development in the summer of 2015. Finally, a huge thanks to all those students and my close friends who reported bugs, gave feedback, and in general supported, promoted, got excited about, and complained about Skedge!
